Turbulence in compact to giant HII regions

### 2022-05-18 strucfunc_paper.tex
Minor edits

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B\obs(r)\) remains flat at a value of \(\approx 2\sigma^2\pos\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.

>>>>

At scales larger than \(L/2\)
we see a variety of different shapes for the structure functions
of our sample regions.
These points are excluded from our model fits but we give
a qualitative description in this section.
In some cases,
such as Carina and Hubble~X,
\(B\obs(r)\) remains flat at a value of \(\approx 2\sigma^2\pos\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.
